\section{Opportunities for Learners}
\begin{comment}
* What can your students do?
** One example (pick one - Fedora & your first-year class)
** Documentation
** Translation
** Gardening
** Bug fixing
** Testing
** Artwork/design
** Marketing/outreach
** Being active and vocal users (use open source in outreach/service projects - for instance, Mo & the Girl Scouts) / advocacy
** Legal/licensing work (very, *very* basic stuff)
** it's the non-programming skills that are usually in most need by these communities, because nobody knows about them / how to do them, so you can almost become domain "experts" in a project
** Creative repurposing - bringing a project into a new domain it wasn't necessarily originally designed for
\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Based on the "Climbing Contributor Mountain" analogy
% from the TOS textbook

\begin{frame} 
\frametitle{what can (your) students do?}
\begin{itemize}
	\item Lurk, watch, and listen.
	\item Use and experiment.
	\item Seek out tips, tweaks, advice.
	\item Collaborate to improve something.
	\item Contribute to driving change forward.
\end{itemize}

\end{frame} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Authentic learning!

\begin{frame} 

\huge
\begin{center}
Legitimate peripheral \alert{participation}.
\end{center}

\end{frame} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Example: Fedora and Matt's first-year class

\begin{frame} 
\frametitle{we need liberal arts contributors!}
\begin{itemize}
	\item Documentation
	\item Translation
	\item Gardening % wiki-gardening, should explain
	\item Bug fixing
	\item Testing % more difficult than you might think
	\item Art and Design
	\item Marketing and Outreach
	\item Advocacy and Teaching % girl scout workshops example
	\item Legal
	\item ...and more
\end{itemize}

\end{frame} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%

% it's the non-programming skills that are usually in most 
% need by these communities, because nobody knows about them
% or how to do them, so you can almost become domain "experts" 
% in a project.

\begin{frame} 
\huge
\begin{center}
In a technological world,
liberal arts students
can be \alert{experts}. % I'm not happy with this. Help?
\end{center}

\end{frame} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Creative repurposing - bringing a project into a new domain 
% it wasn't necessarily originally designed for

\begin{frame} 
\frametitle{Creative repurposing}
\huge
\begin{center}
Bringing a project into a \alert{new domain}
it wasn't originally designed for.
\end{center}
% Would be good to have an example here.

\end{frame} 

